Parsing Tweets into Universal Dependencies

### 2018-04-16 paper.tex
move tokenizer results table to nicer location
Noah

\section{Introduction}
NLP for social media messages is challenging, because domain
adaptation is required, and also because creating annotated datasets
(e.g., treebanks)
for training and evaluation is hard. 
Pioneering work by \citet{Foster:2011:HPT:2908630.2908634} 
annotated 7,630 tokens' worth of tweets according to the
phrase-structure conventions of the Penn Treebank
\citep[PTB;][]{Marcus93buildinga}, enabling conversion to Stanford Dependencies.
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank}),
consisting of 12,149 tokens and largely following conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID}, fairly close to 
\citet{Yamada03statisticaldependency} dependencies (without labels). 
Both annotation efforts were highly influenced by the PTB, whose guidelines
have good grammatical coverage on newswire. However, when it comes
to informal, unedited, user-generated text, the guidelines may leave
many annotation decisions unspecified.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

\subsection{Comparison to PoSTWITA-UD}\label{sec:postwita}
The first Twitter treebank annotated with Universal Dependencies 
was the \mbox{\textit{PosTWITA-UD}} corpus for Italian \citep{sanguinetti-17}, 
which consists of 6,738 tweets (119,726 tokens).
In their convention, tokenization tends to preserve the original
tweet content but two special cases, \textit{articulated prepositions}
(e.g.~\textit{nella} as \textit{in la})
and \textit{clitic clusters} (e.g.~\textit{guardandosi} as \textit{guardando si}), are tokenized.
%\nss{explain what these two phenomena are. are these the only words that are split?}\yjcomment{done}
%Beyond tokenization, an extra layer of lemmas is annotated
%to recover ``what is understandable by a human''.
%It's arguable whether normalization (the lemmatization in \citet{sanguinetti-17})
%on social media data is essential according to \citet{eisenstein:2013:NAACL-HLT}.
%In this paper, we don't include normalization and leave it an open question for further study.
%\nss{Maybe just say: 
Their lemmas include spelling normalization, whereas our lemmas only normalize casing and inflectional morphology.
The current UD guidelines on lemmas are flexible, so variation between treebanks is expected.\footnote{\url{http://universaldependencies.org/u/overview/morphology.html\#lemmas}}
%You could also mention that the current UD guidelines on lemmas (which I wrote) give a lot of flexibility to treebank 
%developers: \url{http://universaldependencies.org/u/overview/morphology.html\#lemmas}}

%In the syntax annotation, tweet specific
%constructions are considered by both \citet{sanguinetti-17} and our paper.
With respect to tweet-specific constructions,
\citeposs{sanguinetti-17} and our  interpretation of headedness is the same, 
but we differ in the relation label.
For topical hashtags, we use \textit{discourse} while \citet{sanguinetti-17} used \textit{parataxis}. 
In referential URLs, we use \textit{list} (following the precedent of UD\_English-EWT) while \citet{sanguinetti-17} used \textit{dep}.
%<<<<<<< HEAD
%The choice of relation on the non-syntactic tokens is questionable
%since UD doesn't specify a convention for this. 
%Our choice of \textit{discourse} is inspired by the observation that emoticon is annotated as \textit{discourse}.
%\citet{sanguinetti-17} used the same relation for the emoticon but analyze topical hashtag as \textit{parataxis}.%\nss{what did PosTWITA-UD use for non-syntactic tokens?}\yjcomment{done}
%=======
%The choice of relation on the non-syntactic tokens is questionable
%since UD doesn't specify a convention for this. 
Our choice of \textit{discourse} for sentiment emoticons
is inspired by the observation that emoticons are annotated as \textit{discourse} by UD\_English-EWT
and \citet{sanguinetti-17} used the same relation for the emoticons.
Retweet constructions and truncated words were not explicitly touched
in \citet{sanguinetti-17}.
Judging from the released treebank\footnote{\url{https://github.com/UniversalDependencies/UD_Italian-PoSTWITA}}, the \textit{RT} marker, at-mention, and colon in the retweet construction are all attached to the predicate of the following sentence with \textit{dep}, \textit{vocative:mention} and \textit{punct}.
%\nss{how does the other treebank treat the RT construction and truncated words?}
%\nss{topical hashtags already mentioned above}
%>>>>>>> a7f86b777a73f64b2f05101f4804421aea0412f3
% Non-syntactic tokens can be easily recovered
% from our annotation and changing it to other relation in the future development is not difficult.
We expect that the official UD guidelines will eventually adopt standards for these constructions so the treebanks can be harmonized.

@@

\subsubsection{Data Collection}
{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1}
(840 unique tweets, 639/201 for training/test), along with an 
additional 210 tweets sampled from the POS-tagged dataset of
\newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled
from the Twitter stream from February 2016 to July 2016.\footnote{Data downloaded from \url{https://archive.org/}.}
The latter data source consists of 147.4M English tweets after being
filtered by the {\it lang} attribute in the tweet JSON and {\it
  langid.py}.\footnote{\url{https://github.com/saffsd/langid.py}}
In the same way as \citet{kong-EtAl:2014:EMNLP2014},
reference unit is always the tweet in its entirety
-- which may thus consist of multiple sentences -- not the sentence alone. %\nss{``Each tweet is annotated with a single tree, rather than being split into sentences.''?}
Before annotation, we use a simple regular expression to anonymize usernames and URLs.

@@

\subsubsection{Annotation Process}
\begin{table}
	\centering
	\begin{tabular}{rrrrr}
%		\hline
		 & \multicolumn{2}{c}{\textsc{Tweebank v1}} & \multicolumn{2}{c}{\textsc{Tweebank v2}} \\
		split & tweets & tokens & tweets & tokens \\
		\hline
		train & 639 & 9,310 & 1,639 & 24,753 \\
		dev & --\hphantom{0} & --\hphantom{00} & 710 & 11,742 \\
		test & 201 & 2,839 & 1,201 & 19,112 \\
		\hline
		total & 840 & 12,149 & 3,550 & 55,607 \\
%		\textsc{v1} & tweets & 639 & 0 & 201 & 840 \\
%		& tokens  & 9,310 & 0 & 2,839 & 12149 \\
%		\hdashline
%		\textsc{v2} & tweets & 1,639 & 709 & 1,201 & 3,549 \\
%		 & tokens &	24,753	&	11,742	&	19,112 & 55,617\\
%		\hline
	\end{tabular}

%	\begin{tabular}{rrrrrr}
%		\hline
%		\multicolumn{2}{l}{version} & train & dev & test & total \\
%		\hline
%		\textsc{v1} & tweets & 639 & 0 & 201 & 840 \\
%		& tokens  & 9,310 & 0 & 2,839 & 12149 \\
%		\hdashline
%		\textsc{v2} & tweets & 1,639 & 709 & 1,201 & 3,549 \\
%		 & tokens &	24,753	&	11,742	&	19,112 & 55,617\\
%		\hline
%	\end{tabular}
\caption{Statistics of {\sc Tweebank v2} and the comparison with
{\sc Tweebank v1} in quantity.
%\nss{not obvious how to interpret this: train tokens looks like 1,609+1,000 = 2,609, but maybe it's 609+1,000=1,609? 
%I think it would be easier just to show v1 and v2 as separate rows. Also, a column for totals across the splits.}
%\yjcomment{i've fix this.}
\label{tbl:data-stat}
}
\end{table}
Our annotation process was conducted in two stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
portion and the additional 210 tweets and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the general UD
annotation conventions and our guidelines specifically for annotating tweets.
Both the guidelines and annotations
were further refined by the authors of this paper to increase
the coverage of our guidelines and solve inconsistencies between
different annotators during this exercise. In the second stage, a tokenizer, a POS tagger, and a
parser were trained on the annotated data from the first stage (1,050 tweets in total),
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data and finally achieved 3,550 labeled tweets.\footnote{Manual annotation was done with Arborator \cite{gerdes:2013:W13-37}, a web platform for drawing dependency trees.}
Newly created annotations are split into train, development, and test sets and appended
to the original splits of {\sc Tweebank v1}. Statistics of our annotations and data splits are shown
in Table~\ref{tbl:data-stat}.

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
%		\hline
		\it System & $F_1$ \\
		\hline
		  Stanford CoreNLP & 97.3 \\
		 Twokenizer & 94.6 \\
% 		UDPipe v1.2 & 94.7 \\
		\hdashline
		UDPipe v1.2 & 97.4 \\
	 	our bi-LSTM tokenizer & 98.3 \\
%		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}
%\citet{wang-EtAl:2017:Long6} show that the parser\nss{tokenizer?}\yjcomment{it's a parsing work.}\nss{I guess I don't follow how parsing results 
%on combined training data affect our decision about how to tokenize.} trained 
%on the combination of the UD\_English and Singapore English dialect (Singlish) treebanks
%outperforms the one trained only on the dialect treebank.  
Our preliminary results
showed that our model trained on
the combination of UD\_English-EWT and \textsc{Tweebank v2}
outperformed the one trained only on the UD\_English-EWT or \textsc{Tweebank v2},
consistent with previous work on dialect treebank parsing \cite{wang-EtAl:2017:Long6}.
So we trained our tokenizer on the training portion of
\textsc{Tweebank v2} combined with the UD\_English-EWT training set
and tested on the \textsc{Tweebank v2} test set. % \yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}\yjcomment{add discussion}
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
 Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540}\footnote{We use the updated version of Twokenizer from \citet{owoputi-EtAl:2013:NAACL-HLT}.} are rule-based systems and were not adapted
to the UD tokenization scheme.
The UDPipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system. Compared with UDPipe, we use an LSTM
instead of a GRU in our model and we also use a larger size for hidden units (64 vs.~20),
which has stronger representational power. 
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results speak to the value of statistical modeling
in tokenization for informal texts.%\nss{this paragraph needs copyediting}

@@

\paragraph{Initial results.}  The first section of Table~\ref{tbl:parse-result} compares
the stack LSTM with {\sc TweeboParser} (the system 
of \citealp{kong-EtAl:2014:EMNLP2014}) and the state-of-the-art parser
in the CoNLL 2017 evaluations, due to
 \citet{dozat-qi-manning:2017:K17-3}.
 \Citeposs{kong-EtAl:2014:EMNLP2014} parser is a graph-based
parser with lexical features and word cluster and it uses dual decomposition
for decoding. The parser in \citet{dozat-qi-manning:2017:K17-3} is also a graph-based parser
but includes character-based word representation and uses a biaffine classifier
to predict if an attachment exists between two words.
Both of the compared systems require superlinear runtime due to graph-based parsing. 
They are re-trained on the same data as our
system.
Our baseline lags behind by nearly two LAS
points but runs faster than both of them.

@@

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We also compare
our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
Stanford CoreNLP tokenizer,\footnote{We choose the Stanford CoreNLP tokenizer in the spirit of comparing 
rule-based and statistical methods.} %\yicomment{why not compare with UDPipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
\citeposs{owoputi-EtAl:2013:NAACL-HLT} tagger, and \citeposs{dozat-qi-manning:2017:K17-3} parser.
Our system differs from the SOTA pipeline in the tokenization and parser components.
From Table \ref{tbl:pipline}, our pipeline outperforms the SOTA when
evaluated in pipeline manner.
The results also emphasize the
importance of tokenization:  without gold tokenization
%\nascomment{changed ``segmentation'' to ``tokenization'' here, twice},
UD parsing
performance drops by about four points.

>>>>

\section{Introduction}
NLP for social media messages is challenging, because domain
adaptation is required, and also because creating annotated datasets
(e.g., treebanks)
for training.
Pioneering work by \citet{Foster:2011:HPT:2908630.2908634} 
annotated 7,630 tokens' worth of tweets according to the
phrase-structure conventions of the Penn Treebank
\citep[PTB;][]{Marcus93buildinga}, enabling conversion to Stanford Dependencies.
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank}),
consisting of 12,149 tokens and largely following conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID}, fairly close to 
\citet{Yamada03statisticaldependency} dependencies (without labels). 
Both annotation efforts were highly influenced by the PTB, whose guidelines
have good grammatical coverage on newswire. However, when it comes
to informal, unedited, user-generated text, the guidelines may leave
many annotation decisions unspecified.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

\subsection{Comparison to PoSTWITA-UD}\label{sec:postwita}
The first Twitter treebank annotated with Universal Dependencies 
was the \mbox{\textit{PosTWITA-UD}} corpus for Italian \citep{sanguinetti-17}, 
which consists of 6,738 tweets (119,726 tokens).
In their convention, tokenization tends to preserve the original
tweet content but two special cases, \textit{articulated prepositions}
(e.g., \textit{nella} as \textit{in la})
and \textit{clitic clusters} (e.g.~\textit{guardandosi} as \textit{guardando si}), are tokenized.
%\nss{explain what these two phenomena are. are these the only words that are split?}\yjcomment{done}
%Beyond tokenization, an extra layer of lemmas is annotated
%to recover ``what is understandable by a human''.
%It's arguable whether normalization (the lemmatization in \citet{sanguinetti-17})
%on social media data is essential according to \citet{eisenstein:2013:NAACL-HLT}.
%In this paper, we don't include normalization and leave it an open question for further study.
%\nss{Maybe just say: 
Their lemmas include spelling normalization, whereas our lemmas only normalize casing and inflectional morphology.
The current UD guidelines on lemmas are flexible, so variation between treebanks is expected.\footnote{\url{http://universaldependencies.org/u/overview/morphology.html\#lemmas}}
%You could also mention that the current UD guidelines on lemmas (which I wrote) give a lot of flexibility to treebank 
%developers: \url{http://universaldependencies.org/u/overview/morphology.html\#lemmas}}

%In the syntax annotation, tweet specific
%constructions are considered by both \citet{sanguinetti-17} and our paper.
With respect to tweet-specific constructions,
\citeposs{sanguinetti-17} and our  interpretation of headedness are the same, 
but we differ in the relation label.
For topical hashtags, we use \textit{discourse} while they used \textit{parataxis}. 
In referential URLs, we use \textit{list} (following the precedent of UD\_English-EWT) while they used \textit{dep}.
%<<<<<<< HEAD
%The choice of relation on the non-syntactic tokens is questionable
%since UD doesn't specify a convention for this. 
%Our choice of \textit{discourse} is inspired by the observation that emoticon is annotated as \textit{discourse}.
%\citet{sanguinetti-17} used the same relation for the emoticon but analyze topical hashtag as \textit{parataxis}.%\nss{what did PosTWITA-UD use for non-syntactic tokens?}\yjcomment{done}
%=======
%The choice of relation on the non-syntactic tokens is questionable
%since UD doesn't specify a convention for this. 
Our choice of \textit{discourse} for sentiment emoticons
is inspired by the observation that emoticons are annotated as \textit{discourse} by UD\_English-EWT;
\citet{sanguinetti-17} used the same relation for the emoticons.
Retweet constructions and truncated words were not explicitly touched
by \citet{sanguinetti-17}.
Judging from the released treebank\footnote{\url{https://github.com/UniversalDependencies/UD_Italian-PoSTWITA}}, the \textit{RT} marker, at-mention, and colon in the retweet construction are all attached to the predicate of the following sentence with \textit{dep}, \textit{vocative:mention} and \textit{punct}.
%\nss{how does the other treebank treat the RT construction and truncated words?}
%\nss{topical hashtags already mentioned above}
%>>>>>>> a7f86b777a73f64b2f05101f4804421aea0412f3
% Non-syntactic tokens can be easily recovered
% from our annotation and changing it to other relation in the future development is not difficult.
We expect that the official UD guidelines will eventually adopt standards for these constructions so the treebanks can be harmonized.

@@

\subsubsection{Data Collection}
{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1}
(840 unique tweets, 639/201 for training/test), along with an 
additional 210 tweets sampled from the POS-tagged dataset of
\newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled
from the Twitter stream from February 2016 to July 2016.\footnote{Data downloaded from \url{https://archive.org/}.}
The latter data source consists of 147.4M English tweets after being
filtered by the {\it lang} attribute in the tweet JSON and {\it
  langid.py}.\footnote{\url{https://github.com/saffsd/langid.py}}
As done by \citet{kong-EtAl:2014:EMNLP2014}, the
annotation unit is always the tweet in its entirety---which may consist of multiple sentences---not the sentence alone. %\nss{``Each tweet is annotated with a single tree, rather than being split into sentences.''?}
Before annotation, we use a simple regular expression to anonymize usernames and URLs.

@@

\subsubsection{Annotation Process}
\begin{table}
	\centering
	\begin{tabular}{rrrrr}
%		\hline
		 & \multicolumn{2}{c}{\textsc{Tweebank v1}} & \multicolumn{2}{c}{\textsc{Tweebank v2}} \\
		split & tweets & tokens & tweets & tokens \\
		\hline
		train & 639 & 9,310 & 1,639 & 24,753 \\
		dev. & --\hphantom{0} & --\hphantom{00} & 710 & 11,742 \\
		test & 201 & 2,839 & 1,201 & 19,112 \\
		\hline
		total & 840 & 12,149 & 3,550 & 55,607 \\
%		\textsc{v1} & tweets & 639 & 0 & 201 & 840 \\
%		& tokens  & 9,310 & 0 & 2,839 & 12149 \\
%		\hdashline
%		\textsc{v2} & tweets & 1,639 & 709 & 1,201 & 3,549 \\
%		 & tokens &	24,753	&	11,742	&	19,112 & 55,617\\
%		\hline
	\end{tabular}

%	\begin{tabular}{rrrrrr}
%		\hline
%		\multicolumn{2}{l}{version} & train & dev & test & total \\
%		\hline
%		\textsc{v1} & tweets & 639 & 0 & 201 & 840 \\
%		& tokens  & 9,310 & 0 & 2,839 & 12149 \\
%		\hdashline
%		\textsc{v2} & tweets & 1,639 & 709 & 1,201 & 3,549 \\
%		 & tokens &	24,753	&	11,742	&	19,112 & 55,617\\
%		\hline
%	\end{tabular}
\caption{Statistics of {\sc Tweebank v2} and  comparison with
{\sc Tweebank v1}.
%\nss{not obvious how to interpret this: train tokens looks like 1,609+1,000 = 2,609, but maybe it's 609+1,000=1,609? 
%I think it would be easier just to show v1 and v2 as separate rows. Also, a column for totals across the splits.}
%\yjcomment{i've fix this.}
\label{tbl:data-stat}
}
\end{table}
Our annotation process was conducted in two stages.
In the first stage, 18 researchers worked on the {\sc Tweebank v1}
portion and the additional 210 tweets and created the initial annotations in one day.
Before annotating, they were given a tutorial overview of the general UD
annotation conventions and our guidelines specifically for annotating tweets.
Both the guidelines and annotations
were further refined by the authors of this paper to increase
the coverage of our guidelines and solve inconsistencies between
different annotators during this exercise. In the second stage, a tokenizer, a POS tagger, and a
parser were trained on the annotated data from the first stage (1,050 tweets in total),
and used to automatically analyze the sampled 2,500 tweets.  Authors 
of this paper manually corrected the parsed data and finally achieved 3,550 labeled tweets.\footnote{Manual annotation was done with Arborator \cite{gerdes:2013:W13-37}, a web platform for drawing dependency trees.}
Newly created annotations are split into train, development, and test sets and appended
to the original splits of {\sc Tweebank v1}. Statistics of our annotations and data splits are shown
in Table~\ref{tbl:data-stat}.

@@

%\citet{wang-EtAl:2017:Long6} show that the parser\nss{tokenizer?}\yjcomment{it's a parsing work.}\nss{I guess I don't follow how parsing results 
%on combined training data affect our decision about how to tokenize.} trained 
%on the combination of the UD\_English and Singapore English dialect (Singlish) treebanks
%outperforms the one trained only on the dialect treebank.  
Our preliminary results
showed that our model trained on
the combination of UD\_English-EWT and \textsc{Tweebank v2}
outperformed the one trained only on the UD\_English-EWT or \textsc{Tweebank v2},
consistent with previous work on dialect treebank parsing \cite{wang-EtAl:2017:Long6}.
So we trained our tokenizer on the training portion of
\textsc{Tweebank v2} combined with the UD\_English-EWT training set
and tested on the \textsc{Tweebank v2} test set. % \yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}\yjcomment{add discussion}
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
 Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540}\footnote{We use the updated version of Twokenizer from \citet{owoputi-EtAl:2013:NAACL-HLT}.} are rule-based systems and were not adapted
to the UD tokenization scheme.
The UDPipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system. Compared with UDPipe, we use an LSTM
instead of a GRU in our model and we also use a larger size for hidden units (64 vs.~20),
which has stronger representational power. 
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results speak to the value of statistical modeling
in tokenization for informal texts.%\nss{this paragraph needs copyediting}

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
%		\hline
		\it System & $F_1$ \\
		\hline
		  Stanford CoreNLP & 97.3 \\
		 Twokenizer & 94.6 \\
% 		UDPipe v1.2 & 94.7 \\
		\hdashline
		UDPipe v1.2 & 97.4 \\
	 	our bi-LSTM tokenizer & 98.3 \\
%		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}

@@

\paragraph{Initial results.}  The first section of Table~\ref{tbl:parse-result} compares
the stack LSTM with {\sc TweeboParser} (the system 
of \citealp{kong-EtAl:2014:EMNLP2014}) and the state-of-the-art parser
in the CoNLL 2017 evaluations, due to
 \citet{dozat-qi-manning:2017:K17-3}.
 \Citeposs{kong-EtAl:2014:EMNLP2014} parser is a graph-based
parser with lexical features and word cluster and it uses dual decomposition
for decoding. The parser in \citet{dozat-qi-manning:2017:K17-3} is also a graph-based parser
but includes character-based word representations and uses a biaffine classifier
to predict whether an attachment exists between two words.
Both of the compared systems require superlinear runtime due to graph-based parsing. 
They are re-trained on the same data as our
system.
Our baseline lags behind by nearly two LAS
points but runs faster than both of them.

@@

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We also compare
our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
Stanford CoreNLP tokenizer,\footnote{We choose the Stanford CoreNLP tokenizer in the spirit of comparing 
rule-based and statistical methods.} %\yicomment{why not compare with UDPipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
\citeposs{owoputi-EtAl:2013:NAACL-HLT} tagger, and \citeposs{dozat-qi-manning:2017:K17-3} parser.
Our system differs from the state-of-the-art pipeline in the tokenization and parser components.
From Table \ref{tbl:pipline}, our pipeline outperforms the state of
the art when
evaluated in pipeline manner.
The results also emphasize the
importance of tokenization:  without gold tokenization
%\nascomment{changed ``segmentation'' to ``tokenization'' here, twice},
UD parsing
performance drops by about four points.
